Adaptive timing of investment strategy

### 2020-05-24 notebook/ms/SI5.Rmd
Get the authors listed in a way that won't run over the PDF

---
title: "Fisheries example integrating FLR"
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy
  Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 5)'
biblio-style: apalike
---

>>>>

---
title: "Fisheries example integrating FLR"
author: |
        | A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;, Jeroen Minderman&#xb9;, 
        | Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy Rakotonarivo&#xb9;, 
        | Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 5)'
biblio-style: apalike
---

### 2020-05-24 notebook/ms/SI7.Rmd
Get the authors listed in a way that won't run over the PDF

---
title: "Default GMSE data structures"
author: |
        | A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;, Jeroen Minderman&#xb9;, 
        | Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy Rakotonarivo&#xb9;, 
        | Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;'
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes: 
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 7)'
biblio-style: apalike
---

>>>>

---
title: "Default GMSE data structures"
author: |
        | A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;, Jeroen Minderman&#xb9;, 
        | Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy Rakotonarivo&#xb9;, 
        | Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes: 
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 7)'
biblio-style: apalike
---

### 2020-05-24 notebook/ms/SI8.Rmd
Get the authors listed in a way that won't run over the PDF

---
title: 'Adaptive timing of investment strategy'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (New function vignette)'
author: Adrian Bach&#xb9; &#xb2;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK [2] adrian.bach@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

>>>>

---
title: 'Adaptive timing of investment strategy'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (New function vignette)'
author: | 
        | Adrian Bach&#xb9; &#xb2;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK [2] adrian.bach@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---
